draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
```

@@

```{r }
lda <- LDA(dfm_, 3)

lda
```

```{r}
library(tidytext)

topic_words <- tidy(lda, matrix="beta") %>% 
  group_by(topic) %>%
  slice_max(beta, n = 3) %>%
  ungroup() %>%
  arrange(topic, -beta)

topic_words

topic_words %>%
  mutate(term = reorder_within(term, beta, topic)) %>% 
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") + scale_y_reordered()
```

@@

text_tokens <- tidy(dfm_corp) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfm_corp) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))

@@

```{r}
library(vader)

sentiments <- vader_df(df$Summary)

@@

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
Library(tidyr)
```

@@

```{r }
#Topics for session 115 (2017 - 2018)

lda_115 <- LDA(dfmat_115, 5)

topic_words_115 <- tidy(lda_115, matrix="beta") %>% 
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  arrange(topic, -beta)

topic_words_115

topic_words_115 %>%
  mutate(term = reorder_within(term, beta, topic)) %>% 
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
```

```{r }
#Topics for session 116 (2019 - 2020)

lda_116 <- LDA(dfmat_116, 5)

topic_words_116 <- tidy(lda_116, matrix="beta") %>% 
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  arrange(topic, -beta)

topic_words_116

topic_words_116 %>%
  mutate(term = reorder_within(term, beta, topic)) %>% 
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
```

```{r }
#Topics for session 117 (2021 - 2022)
raw.sum = apply(dfmat_117,1,FUN=sum) #Removing non-0 rows from dfmat
dfmat_117 = dfmat_117[raw.sum != 0, ]

lda_117 <- LDA(dfmat_117, 5)

topic_words_117 <- tidy(lda_117, matrix="beta") %>% 
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  arrange(topic, -beta)

topic_words_117

topic_words_117 %>%
  mutate(term = reorder_within(term, beta, topic)) %>% 
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") + scale_y_reordered() + theme_minimal()
```

@@

text_tokens <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))

@@

```{r}
df %>%
  is.na(summary)

sentiments <- vader_df(df$summary)

@@

```{r}
library(tidyr)
#tweet_sentiment$date <- as.Date(tweet_sentiment$created)

wide_sentiment <- summary_sentiment %>%
  group_by(partisan, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = partisan, values_from = score)

days <- data.frame(date = seq(as.Date("2017-01-01"),as.Date("2022-12-31"),1))

daily_sentiment <- days %>% 
  left_join(wide_sentiment) %>% 
  pivot_longer(cols = -date, names_to="partisan", values_to="score") %>% 
  group_by(partisan) %>% 
  arrange(date) %>%
  mutate(score7 = data.table::frollmean(score, 7))

daily_sentiment %>% head()

ggplot(daily_sentiment, aes(date, colour=partisan)) +
  geom_point(aes(y=score),size=0.5) + geom_line(aes(y=score7))
```
